---
title: "Use of tximeta with a denovo transcriptome"
author: "Michael Love"
---

This is a project in collaboration with Lisa Johnson and Tessa Pierce
from the lab of Titus Brown.

# Transcript abundance

Transcript abundance was estimated with Salmon and the quantification
directories were collected as a single `.tar.gz` file and deposited to
Zenodo:

* https://zenodo.org/record/1486283#.W-xVBHpKiL8

These were downloaded and extracted to a directory
`Fundulus_rathbuni_salmon`, which contains 9 Salmon output
directories. 

# Attempting import without linking to annotation

```{r}
# install_github("mikelove/tximeta", dependencies=FALSE)
library(tximeta)
dir <- "Fundulus_rathbuni_salmon"
files <- file.path(list.files(dir, full=TRUE), "quant.sf")
all(file.exists(files))
names <- list.files(dir)
names <- sub(".quant","",names)
coldata <- data.frame(files, names)
se <- tximeta(coldata)
```

In the above code chunk, `tximeta` attempts to find a matching
transcriptome in its database but fails, and then returns an
"un-ranged SummarizedExperiment", meaning that we don't have any extra
information about the transcripts. We have the rownames and multiple
matrices of data:

```{r}
suppressPackageStartupMessages(library(SummarizedExperiment))
assayNames(se)
assays(se)[["counts"]][1:4,1:4]
```

